A Formalization of Complete Discrete Valuation Rings and Local Fields

### 2023-12-12 HAL/CPP_paper_v2.tex
fix hm

The local analysis described before is an example of the ``local-to-global'' principle: to solve a problem in $\ZZ$, or $\QQ$, one can try to solve it in $\QQ_p$, for all $p$, and in $\RR$. A famous application of the local-to-global principle is the Hasse–Minkowski Theorem, which states that if $Q(x)$ is a quadratic form with rational coefficients, then the equation $Q(x) =c$ has a nontrivial solution over $\QQ$ if and only if it has a nontrivial solution over $\RR$ and over every $\QQ_p$.

>>>>

The local analysis described before is an example of the ``local-to-global'' principle: to solve a problem in $\ZZ$, or $\QQ$, one can try to solve it in $\QQ_p$, for all $p$, and in $\RR$. A famous application of the local-to-global principle is the Hasse–Minkowski Theorem, which states that if $Q(x)$ is a quadratic form with rational coefficients, then the equation $Q(x)=0$ has a nontrivial solution over $\QQ$ if and only if it has a nontrivial solution over $\RR$ and over every $\QQ_p$.
